Article title

### 2019-07-16 NAR_DRAFT.tex
working on table
small table changes

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date} \cite{Griffith2015}.
We merged the gold and platinum lists, and define as \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.
\subsubsection{What I call the cell paper} Not sure if this will get used.

\subsection{Calibration}
We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-fig1} \textbf{e}).
Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the total area between the result and a diagonal line.
\bkmcomment{Honestly, just putting the R code here exactly as Austin does is probably the best explanation?}

@@

\section{RESULTS}

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}llllllll@{}}
\toprule
Experiment & $\mu$ & AUROC &  & AUPRC & & ICI & 
\\
& & MuTect & Calibrated & MuTect & Calibrated & MuTect & Calibrated
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & -- &&&
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2 &&&
\\
\botrule
\end{tabular*}%
}
{AUROC/AUPRC = area under ROC/PRC curve. ICI = Integrated calibration index}
\end{table*}

>>>>

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date, and primary/relapse distinction} \cite{Griffith2015}.
We merged the gold and platinum lists, and define as \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.
\subsubsection{What I call the cell paper} Not sure if this will get used.

\subsection{Calibration}
We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-fig2}\textbf{b,d}).
Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the total area between the result and a diagonal line.

@@

\section{RESULTS}
\bkmcomment{I can't find a measured mutation rate for aml31. I get 3e-8 which isn't out of line for a leukemia primary.}

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\textwidth}{@{}lllllllll@{}}
\toprule
Depth & Signature & $\mu$ & AUROC &  & AUPRC & & ICI & 
\\
& & & MuTect & Calibrated & MuTect & Calibrated & MuTect & Calibrated
\\
\colrule
100X WGS & Concentrated & Row 1 & Row 1 & -- & -- &&
\\
100X WGS & Intermediate & Row 1 & Row 1 & -- & -- &&
\\
100X WGS & Diffuse & Row 1 & Row 1 & -- & -- &&
\\
500X WES & Concentrated & Row 1 & Row 1 & -- & -- &&
\\
500X WES & Intermediate & Row 1 & Row 1 & -- & -- &&
\\
500X WES & Diffuse & Row 1 & Row 1 & -- & -- &&
\\
AML 31 & Actual & Row 1 & Row 1 & -- & -- &&
\\
\botrule
\end{tabular*}%
}
{$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
\end{table*}
